Time-dependent optimized coupled-cluster method for multielectron dynamics

### 2018-04-14 doc/TimeDependence/Tex/Article.tex
Update on article

\documentclass[a4paper,10pt, twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{braket}
\usepackage{verbatim}
\usepackage{mdframed} %nice frames
\usepackage[hidelinks]{hyperref}
\usepackage{cite}
\usepackage[toc,page]{appendix}
\newtheorem{theorem}{Theorem}
\renewcommand{\thesection}{\Roman{section}}
\renewcommand\thesubsection{\Alph{subsection}}
%opening
\title{Article}
\author{Kristiansen, Håkon Emil}

@@

@@

%\tableofcontents

\section{Introduction}
Quantum mechanics is a theory that describes/models the properties of microscopic systems. It postulates that given the so-called wavefunction, $\Psi(\mathbf{r},t)$, we can 
in principle compute all that there is to know about the system. 
Given suitable initial conditions $\Psi(\mathbf{r},t)$ can be determined for all future time by solving the time-dependent Schrödinger equation (TDSE),
\begin{equation}
 i \hbar \frac{\partial }{\partial t} \Psi(\mathbf{r},t) = \hat{H} \Psi(\mathbf{r},t).
\end{equation}
The initial condition is typically taken as a linear combination of what is called stationary states, which in turn can be found by solving what is known as the 
time-independent Schrödinger (TISE) equation
\begin{equation}
 \hat{H} \Psi(\mathbf{r}) = E \Psi(\mathbf{r}).
\end{equation}
Exact/analytical solutions to the TISE is possible only for the simplest systems and general solutions to the TDSE is even rarer. Thus, 
one must resort to approximative/numerical methods. Of particular interest is the so-called many-body problem where one considers systems of a large number of interacting particles, 
where large can be anywhere from two to infinity.

@@

Similarly, there exists different approximations to the solution of the TDSE with 
the Multiconfiguration Time-Dependent Hartree-Fock method (MCTDHF) being considered the most accurate. MCTDHF, which is combination of CI and HF generalized to 
the time domain, suffers from exponential scaling. In a recent article \cite{Kvaal12}, Simen Kvaal proposes a method based on Coupled-Cluster theory, 
the so-called Orbital Adaptive Time Dependent Coupled Cluster method (OATDCC), which is a hierarchical approximation to the MCTDHF method. The OATDCC inherits 
size-consisteny and extensivity from the CC method and achieves polynomial scaling. 
\section{Theory/Formalism}
\subsection{The model Hamiltonian}
We shall model the quantum dot systems as a collection of $N$ nonrelativistic electrons of mass $m$ in $d$-dimensional space trapped by a confining potential 
$v_{\text{conf}}(\mathbf{\hat{r}})$. Here $\hat{\mathbf{r}}$ is the position operator in $d$-dimensional space 
\begin{equation}
 \hat{\mathbf{r}} \equiv \sum_{i=1}^d \hat{\mathbf{x}}_i \hat{\mathbf{e}}_i
\end{equation}
with $\hat{\mathbf{e}}_i$ a unit vector.

@@

\end{appendices}
\end{comment}
\clearpage
\bibliographystyle{ieeetr}
\bibliography{references}

>>>>

\documentclass[aip,jcp,reprint,floatfix]{revtex4-1}

\usepackage{amsmath,amssymb}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{bbold}
\usepackage{natbib}
\usepackage[normalem]{ulem} % to strike out plain text
\usepackage[colorlinks=true,citecolor={blue},urlcolor={blue}, linkcolor=blue]{hyperref}%
\usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{braket}
\usepackage{verbatim}
\usepackage{mdframed}
\newtheorem{theorem}{Theorem}

@@

\title{Time-dependent optimized coupled-cluster method for multielectron dynamics}

\author{Håkon Emil Kristiansen}
\email[Electronic mail:]{haakoek@student.matnat.uio.no}
\affiliation{Department of Physics, University of Oslo, N-0316 Oslo, Norway}

\pacs{32.80.Rm, 31.15.A-, 42.65.Ky}

@@

\section{Introduction}

Quantum mechanics is a theory that describes/models the properties of
microscopic systems. It postulates that given the so-called
wavefunction, $\Psi(\mathbf{r},t)$, we can in principle compute all
that there is to know about the system.  Given suitable initial
conditions $\Psi(\mathbf{r},t)$ can be determined for all future time
by solving the time-dependent Schrödinger equation (TDSE),
\begin{equation}
 i \hbar \frac{\partial }{\partial t} \Psi(\mathbf{r},t) = \hat{H} \Psi(\mathbf{r},t).
\end{equation}
The initial condition is typically taken as a linear combination of what is called stationary states, which in turn can be found by solving what is known as the 
time-independent Schrödinger (TISE) equation
\begin{equation}
 \hat{H} \Psi(\mathbf{r}) = E \Psi(\mathbf{r}).
\end{equation}
Exact/analytical solutions to the TISE is possible only for the
simplest systems and general solutions to the TDSE is even
rarer. Thus, one must resort to approximative/numerical methods. Of
particular interest is the so-called many-body problem where one
considers systems of a large number of interacting particles, where
large can be anywhere from two to infinity.

@@

Similarly, there exists different approximations to the solution of
the TDSE with the Multiconfiguration Time-Dependent Hartree-Fock
method (MCTDHF) being considered the most accurate. MCTDHF, which is
combination of CI and HF generalized to the time domain, suffers from
exponential scaling. In a recent article \cite{Kvaal12}, Simen Kvaal
proposes a method based on Coupled-Cluster theory, the so-called
Orbital Adaptive Time Dependent Coupled Cluster method (OATDCC), which
is a hierarchical approximation to the MCTDHF method. The OATDCC
inherits size-consisteny and extensivity from the CC method and
achieves polynomial scaling.

\section{Theory/Formalism}
\subsection{The model Hamiltonian}
We shall model the quantum dot systems as a collection of $N$
nonrelativistic electrons of mass $m$ in $d$-dimensional space trapped
by a confining potential $v_{\text{conf}}(\mathbf{\hat{r}})$. Here
$\hat{\mathbf{r}}$ is the position operator in $d$-dimensional space
\begin{equation}
 \hat{\mathbf{r}} \equiv \sum_{i=1}^d \hat{\mathbf{x}}_i \hat{\mathbf{e}}_i
\end{equation}
with $\hat{\mathbf{e}}_i$ a unit vector.

@@

\end{appendices}
\end{comment}
\bibliographystyle{ieeetr}
\bibliography{references}
